Video Understanding : A review of action detection-recognition dataset

### 2024-02-21 paper.tex
added 3 more datasets
.

% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[utf8]{vietnam}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage{tabularx,booktabs}
\usepackage{relsize}
\usepackage{multicol}
\usepackage{etoolbox}%
\usepackage{xpatch}
\usepackage{blindtext}
\usepackage[a4paper,margin=1in,footskip=0.25in]{geometry}
\usepackage{indentfirst}
\setlength{\parindent}{1.5cm}
\setlength{\parskip}{0.5em}
% defined centered version of "X" column type:
\newcolumntype{C}{>{\centering\arraybackslash}X} 
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
		T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\begin{table}[h]
	\centering
	%\small
	\caption{Action recognition dataset}
	\begin{tabular}{l|l l l l l l l l l}
		\toprule
		tên & phân loại(như trong sheet) & temporal & spatial & classification-only & Focus on (scale/diverse class ...) \\
	\end{tabular}%
	\label{config1}
\end{table}%

@@

\begin{table}[h]
	\centering
	%\small
	\caption{Action recognition dataset}
	\begin{tabular}{l|l l l l l l l l l}
		\toprule
		tên & pp tạo act list & nguồn vid & pp anno & các tool anno được sử dụng \\
	\end{tabular}%
	\label{config}
\end{table}%

@@

\section{References}
\end{document}

>>>>

% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{pifont}
\usepackage[utf8]{vietnam}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage{tabularx,booktabs}
\usepackage{relsize}
\usepackage{multicol}
\usepackage{etoolbox}%
\usepackage{xpatch}
\usepackage{blindtext}
\usepackage[a4paper,margin=1in,footskip=0.25in]{geometry}
\usepackage{indentfirst}
\setlength{\parindent}{1.5cm}
\setlength{\parskip}{0.5em}
% defined centered version of "X" column type:
\newcolumntype{C}{>{\centering\arraybackslash}X} 
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
		T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

\begin{table}[h]
	\centering
	%\small
	\caption{Action recognition dataset}
	\renewcommand{\arraystretch}{1.5}
	\begin{tabular}{l|c c c c l l l l l}
		\toprule
		Name & Actor-Action & Temporal & Spatial & Classification & Category \\
		\hline
		HMDB51               & 1 - 1 & \xmark & \xmark & \cmark & Outdoor \\
		UCF101               & 1 - 1 & \xmark & \xmark & \cmark & Number of actions \\
		Sport-1M             & n - 1 & \xmark & \xmark & \cmark & Large scale \\
		ActivityNet          & 1 - 1 & \cmark & \xmark & \xmark & Number of actions \\ 
		Youtube-8M           & n - 1 & \\
		Something Something  & 1 - 1 & \xmark & \xmark & \cmark & Context information \\
		Charades             & 1 - 1 & \cmark & \xmark & \xmark & Daily activity \\
		AVA                  & n - n & \cmark & \cmark & \xmark & \\
		Moments in Time      & 1 - 1 & \xmark & \xmark & \cmark & \\
		HACS                 & 1 - 1 & \cmark & \xmark & \cmark & \\
		HVU                  &       & \xmark & \xmark & \cmark & \\
		AViD                 &       & \xmark & \xmark & \cmark & \\
		\bottomrule

	\end{tabular}%
	\label{config1}
\end{table}%

@@

\begin{table}[h]
	\centering
	%\small
	\caption{Action recognition dataset}
	\renewcommand{\arraystretch}{1.5}
	\begin{tabular}{l|l l l l l l l l l}
		\toprule
		Name & ActMethod & Sourced & Annotate Method & Ann Tools \\
		\hline
		HMDB51               &  \\
		UCF101               &  \\
		Sport-1M             &  \\
		ActivityNet          &  \\ 
		Youtube-8M           &  \\
		Something Something  &  \\
		Charades             &  \\
		AVA                  &  \\
		Moments in Time      &  \\
		HACS                 &  \\
		HVU                  &  \\
	\end{tabular}%
	\label{config6}
\end{table}%

@@

\section{References}

\bibliographystyle{ieeetr}
\bibliography{references.bib}
\end{document}
